### 2025-06-06 short/sections/selected-papers.tex
Update selected-papers.tex

\begin{benumerate}{13}

\item{González-Bustamante, B. (2025, {\itshape forthcoming}). Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval. {\itshape Public Opinion Quarterly}. Preprint upon request.}\vspace{1mm}

@@

\item{González-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010. {\itshape Política y Gobierno, XXV}(1), 31--64. {\scshape url:} \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}

>>>>

\begin{benumerate}{14}

\item{Kantorowicz, J., \& González-Bustamante, B. (2025, {\itshape forthcoming}). Changing Meaning of the Rule of Law. OSF: \href{https://doi.org/10.31219/osf.io/2kzpj}{\textcolor{blue}{10.31219/osf.io/2kzpj}}.}\vspace{1mm}

\item{González-Bustamante, B. (2025, {\itshape forthcoming}). Blame-Shifting in Presidential Systems: Corrective Effect of Ministerial Terminations on Approval. {\itshape Public Opinion Quarterly}. SocArXiv: \href{https://doi.org/10.31235/osf.io/37ruy_v1}{\textcolor{blue}{10.31235/osf.io/37ruy\_v1}}.}\vspace{1mm}

@@

\item{González-Bustamante, B., \& Garrido-Vergara, L. (2018). Socialización, trayectorias y poscarrera de ministros en Chile, 1990-2010. {\itshape Política y Gobierno, XXV}(1), 31--64. URL: \href{http://www.politicaygobierno.cide.edu/index.php/pyg/article/view/1080}{\textcolor{blue}{www.politicaygobierno.cide.edu}}.}\vspace{1mm}
